Object naming is context dependent - A case study on testing linguistic hypotheses on real-world image corpora

### 2018-07-12 papers/SiVL2018/sivl_2018_6pages.tex
some missing refs
small modifications

So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
 State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet (REF!!), though see work by Deng et al. on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
 concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independentl of the visual context.
 %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.

@@

In this Section we discuss the requirements for  being able to study the context dependence of object names to real-world images, inspired by \cite{graf2016animal}'s study.
 Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus. 
Given a real-world scene with multiple objects and a target object that has to be named, we need access to:

@@

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases that follows a consistent taxonomy: its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
Many state-of-the-art object recognizers are trained on a subsample of ImageNet.
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset), such that no (or very few) distractors objects.

@@

\clearpage
\bibliographystyle{splncs}
\bibliography{naming}
\end{document}

>>>>

So far, research in computer vision, and vision \& language, has mostly worked around the fact that objects can be categorized and named at different levels of specificity.
 State-of-the-art object recognizers are typically trained on a flat set of categories taken from ImageNet, cf.\ \cite{googlenet}, though see work by Deng et al. on trading off object recognition accuracy and level of specificity \cite{deng2012hedging}.
\cite{Ordonez:2016} present one of the few explicit studies on naming in computer vision and operationalize the task as translating between leaf nodes in the ImageNet hierarchy and entry-level
 concepts, adopting the traditional view that there is a single preferred name for a given object that can be determined independently of the visual context.
 %Thus, establishing whether object naming is context dependent in realistic, large-scale data sets would not only be of interest to theoretical work on concepts and pragmatics, it would also be of great importance for the design of models in computer vision, object recognition and vision \& language.

@@

In this Section we discuss the requirements for  being able to study the context dependence of object names in real-world images, inspired by \cite{graf2016animal}'s study.
 Figure \ref{fig:graf_genome} shows  \cite{graf2016animal}'s carefully controlled experimental conditions with isolated objects arranged in a collage, and a real-world scene where multiple objects occur in a natural context from Visual Genome \cite{krishna2016visualgenome}.
Thus, in contrast to \cite{graf2016animal} we do not aim for assembling controlled and, to some extent, artificial scenes, meaning that we need to be able to quantify contextual factors for naming in a real-world image corpus. 
Given a real-world scene with multiple objects and a target object that has to be named, we need access to:

@@

ImageNet \cite{imagenet_cvpr09} is one of the biggest publicly available image databases and many state-of-the-art object recognizers are trained on a subsample of its categories. ImageNet follows a consistent taxonomy as its hierarchical organization is based on WordNet \cite{fellbaum1998wordnet}, such that many synsets from WordNet can be queried for visual instances.
Vice versa, given a leaf node in the ImageNet hierarchy, all its specific and more general names can be retrieved by following the links between synsets in WordNet (as is actually done by \cite{Ordonez:2016}).
However, the database is not directly usable for our purposes as each image only depicts a single object (i.e. an instance of the synset) without any (or very few) distractors objects in context.

@@

\clearpage
\bibliographystyle{splncs}
\begin{footnotesize}
\bibliography{naming}
\end{footnotesize}

\end{document}
